### 2022-03-28 manuscript.tex
tubafigures [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/6ce46beb9b9bdd026566d5964739adcd80c051cb.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/6ce46beb9b9bdd026566d5964739adcd80c051cb/checks
https://github.com/scherzerthesis/thesis/actions/runs/2052795565

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/78ef3a4ef4a18353bcca1019ff69fe0e3876a2bc/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/78ef3a4ef4a18353bcca1019ff69fe0e3876a2bc}{scherzerthesis/thesis@78ef3a4}
on March 27, 2022.

@@

\textbf{Animal husbandry}All mice were housed in an environmentally controlled room, and all animal care and experimental procedures were approved by (and in accordance with) the Institutional Animal Care and Use Committee Office of the Huntsman Cancer Institute at the University of Utah. Genetically engineered mouse breeding and genotyping was conducted as previously described (van Veen \emph{et al.}, 2019). The BRAF\textsuperscript{CAT} and \emph{Trp53\textsuperscript{fl/fl}} mice were previously described (Jonkers \emph{et al.}, 2001; van Veen \emph{et al.}, 2019; Dankort \emph{et al.}, 2007; Shai \emph{et al.}, 2015). All viruses were administered in a Biosafety Level 2+ room, as is regulated by the Institutional Biosafety Committee Guidelines. Adeno-SPC-CRE virus (University of Iowa) was delivered through nasal instillation. The \emph{Trp53\textsuperscript{wmR172H}} and \emph{Trp53\textsuperscript{wmR245W}} mice and respective genotyping protocols were gifted by Gigi Lozano and her laboratory and previously published (Zhang \emph{et al.}, 2018; Kim \emph{et al.}, 2021).

\textbf{Cell line generation}Tumor bearing mice were euthanized and lungs dissected. Lungs were then minced and incubated in digestive enzymes Collagenase I, dispase, elastase, for 30 minutes at 37 degrees. Single-cell suspensions were then resuspended in complete DMEM medium and filtered through a 100 micron filter and centrifuged at 300 x g for 5 minutes. Single-cell suspensions were then incubated in red blood cell lysis buffer for 5 minutes at room temperature, then resuspended in complete RPMI and placed in a tissue culture incubator. Cells were then passaged once a week with differential trypsinization to purify tumors cells from viable stromal cells. p53 status and BRAF\textsuperscript{V600E} status (tdTomato+) were assessed by western blot and flow cytometry.

\textbf{Tissue culture}Murine tumor derived cell lines and HCC-3564 cells were routinely cultured in DMEM supplemented with 10\% heat-inactivated FBS and 1\% penicillin/streptomycin. Cells were routinely tested for mycoplasma.

@@

\textbf{Immunohistochemistry and immunofluoresence}Immunohistochemistry was performed as previously described, with the rabbit primary antibody against P53, SPC, phospho-ERK1/2, NKX2-1, HMGA2, p19/ARF (Mollaoglu \emph{et al.}, 2017; van Veen \emph{et al.}, 2019).

\textbf{Slide imaging and Quantification}Hematoxylin and eosin (H\&E) and IHC stained slides 1 were scanned automatically by the 3D Histech Pannoramic MIDI scanner (Thermo Fisher). Slides were imaged and analyzed using Caseviewer Software or QuantCenter analytical center provided on the 3D Histech Slide Scanner at the indicated magnification. Tumor burden was manually calculated on each lung lobe and total tumor area was compared to total lung area. Tumor diameters were measured using QuantCenter software from 3D Histech.

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/6ce46beb9b9bdd026566d5964739adcd80c051cb/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/6ce46beb9b9bdd026566d5964739adcd80c051cb}{scherzerthesis/thesis@6ce46be}
on March 28, 2022.

@@

\textbf{Animal Husbandry} All mice were housed in an environmentally controlled room, and all animal care and experimental procedures were approved by (and in accordance with) the Institutional Animal Care and Use Committee Office of the Huntsman Cancer Institute at the University of Utah. Genetically engineered mouse breeding and genotyping was conducted as previously described (van Veen \emph{et al.}, 2019). The BRAF\textsuperscript{CAT} and \emph{Trp53\textsuperscript{fl/fl}} mice were previously described (Jonkers \emph{et al.}, 2001; van Veen \emph{et al.}, 2019; Dankort \emph{et al.}, 2007; Shai \emph{et al.}, 2015). All viruses were administered in a Biosafety Level 2+ room, as is regulated by the Institutional Biosafety Committee Guidelines. Adeno-SPC-CRE virus (University of Iowa) was delivered through nasal instillation. The \emph{Trp53\textsuperscript{wmR172H}} and \emph{Trp53\textsuperscript{wmR245W}} mice and respective genotyping protocols were gifted by Gigi Lozano and her laboratory and previously published (Zhang \emph{et al.}, 2018; Kim \emph{et al.}, 2021).

\textbf{Tuba-Seq} \emph{Braf\textsuperscript{CAT/+}} and \emph{H11b\textsuperscript{LSL-CAS9/+}} mice have been described(van Veen \emph{et al.}, 2019; Chiou \emph{et al.}, 2015) and maintained on a mixed background. approximetley equal numbers ofmale and female mice were used in the study. lung tumors were initiated by intratracheal intubation of lentiviral Cre vectors as previously described(DuPage \emph{et al.}, 2009). Barcoded lentiviral vectors were supplied by Monte Winslow as previously described(Winters \emph{et al.}, 2017). Briefly, Lentiviral vectors that contain an eight nucleotide sequence that defines the CRISPR-targeted followed by a 15 nucleotide sequence that is unique only to each initiated tumor. Lentivirus was generated in HEK 293T cells in DMEM supplemented with 10\% FBS by standard lentiiral generation and titered as previously described(Winters \emph{et al.}, 2017). Genomic DNA was isolated from bulk lung tissue after weighing. Briefly, benchmark control cell lines were spiked-in to enable calculation of the absolute number of tumor cells from the number of barcode reads. After tissue homogenization and 12-hour proteinase-K digestion, genomic DNA isolation was extracted using standard Phenol-Chloroform and precipitated by ethanol. Suquencing libraries were prepared by PCR amlifying the sgRNA-BC sequencing in eight reactions in parallel with Q5 master mix and purified with AMPure beads and quantified with the Qubit instrument. Computational analysis was performed in house by the Monte Winslow laboratory.

\textbf{Cell Line Generation}Tumor bearing mice were euthanized and lungs dissected. Lungs were then minced and incubated in digestive enzymes Collagenase I, dispase, elastase, for 30 minutes at 37 degrees. Single-cell suspensions were then resuspended in complete DMEM medium and filtered through a 100 micron filter and centrifuged at 300 x g for 5 minutes. Single-cell suspensions were then incubated in red blood cell lysis buffer for 5 minutes at room temperature, then resuspended in complete RPMI and placed in a tissue culture incubator. Cells were then passaged once a week with differential trypsinization to purify tumors cells from viable stromal cells. p53 status and BRAF\textsuperscript{V600E} status (tdTomato+) were assessed by western blot and flow cytometry.

\textbf{Tissue Culture}Murine tumor derived cell lines and HCC-3564 cells were routinely cultured in DMEM supplemented with 10\% heat-inactivated FBS and 1\% penicillin/streptomycin. Cells were routinely tested for mycoplasma.

@@

\textbf{Immunohistochemistry and Immunofluoresence}Immunohistochemistry was performed as previously described, with the rabbit primary antibody against P53, SPC, phospho-ERK1/2, NKX2-1, HMGA2, p19/ARF (Mollaoglu \emph{et al.}, 2017; van Veen \emph{et al.}, 2019).

\textbf{Slide Imaging and Quantification}Hematoxylin and eosin (H\&E) and IHC stained slides 1 were scanned automatically by the 3D Histech Pannoramic MIDI scanner (Thermo Fisher). Slides were imaged and analyzed using Caseviewer Software or QuantCenter analytical center provided on the 3D Histech Slide Scanner at the indicated magnification. Tumor burden was manually calculated on each lung lobe and total tumor area was compared to total lung area. Tumor diameters were measured using QuantCenter software from 3D Histech.

@@

\leavevmode\vadjust pre{\hypertarget{ref-1EwtuJJw6}{}}%
Chiou,S.-H. \emph{et al.} (2015) \href{https://doi.org/10.1101/gad.264861.115}{Pancreatic cancer modeling using retrograde viral vector delivery and in vivo CRISPR/Cas9-mediated somatic genome editing.} \emph{Genes Dev}, \textbf{29}, 1576--85.
